\cvsection{Professional experiences}

\begin{cventries}
  \cventry
    {Blockchain DevOps engineer} % Job title
    {Independant} % Organization
    {Paris} % Location
    {April 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      {
        \item {R\&D, deployment and maintenance of a Kubernetes-based validator nodes infrastructure.}
        \item {Technologies used: TrueNAS, Kubernetes, ArgoCD. Hybrid deployments between cloud providers and on-premise.}
        \item {Major Kubernetes apps used : Istio, Grafana, Loki, Prometheus, Sealed-secrets, Ingress-hub (custom app), cert-manager, nginx ingress}
      }
      \end{cvitems}
    }
    \cventry
      {Double roles : Tech lead for blockchain-based IP protection service | DevOps and internal trainer} % Job title
      {Smart-chain} % Organization
      {Paris} % Location
      {June 2021 - April 2022} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        {
          \item {\underline{Tech lead} : Audit and complete refactor of an in-house blockchain signature/IP protection service :\\several clients in production at my arrival, a few more corporate accounts using the new version (\href{https://www.musicstart.com/}{https://www.musicstart.com/})}
          \item {\underline{API development} and integration in the new infrastructure (\textbf{Python, Helm, networking}) :\\Clients using the new version : Edith-et-Nous, SACEM with \href{https://www.musicstart.com/}{Musicstart}}
          \item {\underline{DevOps} : Self-training on several DevOps technologies :\\\textbf{Docker, Kubernetes, Helm, ArgoCD, S3 bucket, Hashicorp Vault}... Cloud hosting with Scaleway and OVH}
          \item {Deployment, maintenance, updates and migrations of applications in multiple clusters for testing, staging and production stages.}
          \item {\underline{Docker training} Internal Docker training of Full Stack and front-end developpers : \textbf{Best practices, build time and image size optimizations, security concerns...}}
        }
        \end{cvitems}
      }

  \cventry
    {IT networking instructor} % Job title
    {Learneo} % Organization
    {Rue de Clignancourt, Paris} % Location
    {April 2019 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      {
        \item {\underline{Cisco instructor} (CCNA, CCNP R\&S), a couple of one-week training sessions per month, with 2-4 corporate clients at a time.}
        \item {\underline{Huawei} (HCIA R\&S, HCIP R\&S) 2 training sessions spanning a week each, with 2-3 clients.}
        \item {\underline{MIIT project instructor} : networking classes for people in professional conversion. Spanning 3 months, with 15-20 trainees.\\My favorite job thus far.}
        \item {\underline{Infrastructure instructor for RTE-Orange} (ICX) : one-week training for Orange employees.}
      }
      \end{cvitems}
    }

  \cventry
    {Computer science intern} % Job title
    {Mission Locale Orly-Choisy} % Organization
    {Orly, France} % Location
    {May 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of an SMS appointment reminder app (\textbf{Java JEE - Tomcat, Google API, Vianett API})}
        \item {Internal audit of GDPR compliance}
      \end{cvitems}
    }
\end{cventries}
